Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-19 Thesis/04-chap4.qmd
add start of abstract and revised first paragraph of intro

@@

Regression analysis is a fundamental statistical technique widely used in various fields. In modern practice, this analysis is often performed using specialized statistical software, with R being a popular choice among researchers and data analysts. The Comprehensive R Archive Network (CRAN) [@hornik2012comprehensive] hosts a vast array of packages, many of which provide graphical tools for diagnosing residuals in linear regression models. These packages can be broadly categorized into three groups.

>>>>

Regression software is widely available today, but tools for effective diagnostics are still lagging. Although it is advised to diagnose a linear model by plotting residuals, it required human effort which can be prohibit the efforts. Here we describe a new R package that includes a computer vision model for automated assessment of residual plots, and an accompanying shiny app for ease of use.

@@

Regression analysis is a fundamental statistical technique widely used for modeling data from many fields. In modern practice, software for regression analysis tools is widely. The Comprehensive R Archive Network (CRAN) [@hornik2012comprehensive] hosts a vast array of packages, many of which diagnosing models using residual plots. These packages can be broadly categorized into three groups: general purpose, enhanced diagnostics, diagnostics with statistical testing.
